The role of advection versus diffusion in intraventricular transport

### 2025-02-17 paper/main.tex
Fig5: add tangential force contribution bar plot

The CSF velocities are most strongly
affected when removing cilia in the dorsal diencephalic ventricle,
as the maximum velocity magnitude drops from 27.7 \textmu m/s to 8.0 \textmu m/s.
\emph{In vivo}, these cilia generate the strongest flow at
this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
In contrast, removing telencephalic and ventral diencephalic cilia has minimal
impact and results in maximum speeds of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
Changes in the transport dynamics of Dendra2 are most prominent when removing the dorsal cilia
in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
exhibit changes in the dynamics of $\cbar$ (\Cref{fig:fig5}b).
Compared to the baseline model results, we observe a slower increase and lower final concentration
in the middle and anterior ventricles (ROIs 2--5),
and more rapid transport to the posterior ventricle (ROI 6).
In contrast, removal of telencephalic cilia does not alter the evolution of the
mean concentration $\cbar$ with time (\Cref{fig:fig5}b).
Finally, without ventral cilia in the diencephalic ventricle,
more solute spreads towards the anterior ventricle (ROI 5) and
less solute spreads towards the posterior ventricle (ROI 6).
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
    \caption{\textbf{a.} The three separate ciliated regions cilia paralysis is simulated
    by imposing a zero tangential traction boundary condition in the respective region.
    \textbf{b.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
    paralysis scenarios considered. The region named in the legend is the region
    where we modify the cilia tangential traction boundary condition to a free-slip condition
    in the CSF flow model.}
    \label{fig:fig5}
\end{figure}

>>>>

The CSF velocities are most strongly
affected when removing cilia in the dorsal diencephalic ventricle,
as the maximum velocity magnitude drops from 27.7 \textmu m/s to 8.0 \textmu m/s.
\emph{In vivo}, these cilia generate the strongest flow at
this developmental stage of the fish~\cite{Olstad2019CiliaryDevelopment}.
In contrast, removing telencephalic and ventral diencephalic cilia has minimal
impact and results in maximum speeds of 27.7 \textmu m/s or 27.2 \textmu m/s, respectively.
Of the total tangential force exerted by the cilia, ventral cilia in the middle ventricle
contribute with 34\%, while the dorsal cilia exert 52\% of the total tangential
force~(\Cref{fig:fig5}b). The magnitude of the force contributions are thus
more similar than the difference in their impact on the maximum velocity magnitudes.

Changes in the transport dynamics of Dendra2 are most prominent when removing the dorsal cilia
in the diencephalic ventricle. All ROIs (except ROI 1, where we impose the photoconversion curve)
exhibit changes in the dynamics of $\cbar$ (\Cref{fig:fig5}c).
Compared to the baseline model results, we observe a slower increase and lower final concentration
in the middle and anterior ventricles (ROIs 2--5),
and more rapid transport to the posterior ventricle (ROI 6).
In contrast, removal of telencephalic cilia does not alter the evolution of the
mean concentration $\cbar$ with time (\Cref{fig:fig5}c).
Finally, without ventral cilia in the diencephalic ventricle,
more solute spreads towards the anterior ventricle (ROI 5) and
less solute spreads towards the posterior ventricle (ROI 6).
\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{graphics/figure5_compare_cilia_modifications.png}
    \caption{\textbf{a.} The three separate ciliated regions cilia paralysis is simulated
    by imposing a zero tangential traction boundary condition in the respective region.
    \textbf{b.} The total tangential force applied through the tangential traction
    boundary condition in the three separate ciliated regions.
    \textbf{c.} Mean concentration $\cbar(t)$ for the six regions of interest (ROIs) in the three 
    paralysis scenarios considered. The region named in the legend is the region
    where we modify the cilia tangential traction boundary condition to a free-slip condition
    in the CSF flow model.}
    \label{fig:fig5}
\end{figure}
